Regular singular Volterra equations on complex domains

### 2023-07-27 reg-sing-volterra.tex
Work on setting and results; add level-1 ODE example

% hat tip TeX.SE user marsupilam - https://tex.stackexchange.com/a/351570/6934
%%\tikzfading[
%%  name=radial,
%%  inner color=transparent!0,
%%  outer color=transparent!100
%%]
% hat tip TeX.SE user Andrew Stacey
%   https://tex.stackexchange.com/a/82503/6934
%   https://tex.stackexchange.com/questions/82425/tikz-radial-shading-of-a-ring#comment176908_82503
\pgfdeclareradialshading{infinifade}{\pgfpointorigin}{%
  color(0bp)=(transparent!0);
  color(20bp)=(transparent!0);
  color(22bp)=(transparent!10);
  color(24bp)=(transparent!90);
  color(25bp)=(transparent!100)
}
\pgfdeclarefading{infinity}{\pgfuseshading{infinifade}}%

%%\theoremstyle{definition}
\newtheorem{defn}{Definition}
\theoremstyle{plain}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{rmk}{Remark}

% format lists
\setlist[itemize]{leftmargin=15mm}
\makeatletter
% hat tip TeX.SE user31729
%   https://tex.stackexchange.com/a/328393/6934
\newcommand{\cond}[1]{\item[(\textsc{#1})]\protected@edef\@currentlabel{\textsc{#1}}}
\makeatother

@@

If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically. \textbf{[...]}
\subsection{Setting}
\subsubsection{The domain}\label{setting:domain}
Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$. For some of our results, we'll need an extra condition on $\domain$:
\begin{itemize}
\cond{star}\label{cond:star} The set $\domain$ is star-shaped around $\zeta = 0$. In other words, for any $a \in \domain$, a straight path from $\zeta = 0$ to $a$ stays in $\domain$. Since $\domain$ doesn't contain $\zeta = 0$, we'll always leave that starting point out of the path.
\end{itemize}
For the applications we have in mind, $\domain$ might look something like the set pictured below, which satisfies Condition~\eqref{cond:star}.
\begin{center}
\begin{tikzpicture}
\newcommand{\spill}{4}
\fill[violet!20, bezier bounding box, path fading=infinity]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (160:\spill)
  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
  arc (-60:-130:\spill) -- (0, 0);
\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = 0$};
\end{tikzpicture}
\end{center}
\subsubsection{The prototype operator}\label{setting:basic}
The prototypical example of the kind of operator we'll be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel and a regular singularity at $\zeta = 0$.

Being a holomorphic Volterra operator means that $\hardpart$ sends each holomorphic function $\varphi$ on $\domain$ to a new holomorphic function
\[ [\hardpart\,\varphi](a) = \int_{\zeta = 0}^a \hardker(a, \cdot)\,\varphi\;d\zeta. \]
Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We'll suppose this product can be written as a ratio
\[ \hardker(a, a') = \frac{q(a')}{p(a)}, \]
where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means that for some constant $\tau$---the {\em residue} of the singularity---the difference
\[ -\frac{\tau}{\zeta(a)} - \hardker(a, a') \]
is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\Omega^2$. We'll assume that $\tau$ is real and positive.

Our definition of a regular singularity implies that as $|\zeta|$ goes to zero, $|p|$ also goes to zero, while $|q|$ settles into a compact interval that doesn't include zero.
\begin{verify}
[\textit{Proof.} Fix any $a'$ in the neighborhood where the difference above is bounded. By confining $a$ to small enough neighborhoods of $\zeta = 0$, we can make $|\tau/\zeta(a)|$ arbitrarily large, forcing $|q(a')/p(a)|$ to become arbitrarily large to satisfy the definition. Since $a'$ is fixed, the only way for this ratio to get arbitrarily large is for $|p(a)|$ to get arbitrarily small.]
\end{verify}
For some of our results, we'll also need to keep $|p|$ and $|q|$ under control as $|\zeta|$ goes to infinity.
\begin{itemize}
\cond{slow}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
\begin{align*}
\left|\frac{1}{p}\right| & \le e^{\lambda_p |\zeta|} &
\left|\frac{q}{p}\right| & \le \lambda_\text{ratio}
\end{align*}
outside some neighborhood of $\zeta = 0$ in $\Omega$. Note that this only constrains the ratio of $p$ and $q$ when they're evaluated at the same point.
\end{itemize}
This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}. As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
\subsubsection{The perturbed operator}
\subsection{Main results}
%%\begin{defn}\label{fin-order}
%%Consider a Volterra operator $\mathcal{V}$ of the form
%%\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
%%We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
%%\begin{itemize}
%%\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
%%\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
%%\end{itemize}
%%and at one of the following holds:
%%\begin{enumerate}
%%\item\label{case:0th-order} $m$ isn't the zero function.
%%\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
%%\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
%%where {\rm ``diag''} means the diagonal in $\Omega^2$.
%%\end{enumerate}
%%We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
%%\end{defn}
\begin{thm}
For the regular singular Volterra equation
\[ f = \hardpart f \]
given by an operator of the kind described in Section~\ref{setting:basic}, we have the {\em prototype solution}
\begin{equation}\label{eqn:test_solution}
f_0(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.

The size $|f_0|$ goes like $|\zeta|^{\tau-1}$ as $\zeta$ goes to $0$. More precisely, as $|\zeta|$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.

If $\hardpart$ satisfies Condition~\eqref{cond:slow} from Section~\ref{setting:basic}, then $f_0$ is uniformly of exponential type $\lambda$ \textcolor{orange}{[explain what we mean by ``uniformly'']}. In light of the behavior at $\zeta = 0$ described above, this tells us that for every $\Lambda > \lambda$, the solution $f_0$ belongs to the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}
\begin{thm}
\textcolor{DarkTurquoise}{Existence and uniqueness for deformed operator}
\end{thm}
\textcolor{DarkTurquoise}{The result below might not be stated perfectly, but it gives at least a rough sense of what I expect. It's an improved version of the result stated in Section~\ref{frac_int_exist}, which is copied from {\tt airy-resurgence}. Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}
\color{RoyalBlue}
\begin{thm}
Let $\Omega$ be an acute-angled open sector around $\zeta = 0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.} Over $\Omega$, consider a Volterra operator
\[ \mathcal{P} = p + \partial^{-1} \circ q + \mathcal{R}, \]
where
\begin{itemize}
\item $p$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
\begin{itemize}
\item a simple zero at $\zeta = 0$,
\item no zeros in $\Omega$ (as the next condition implies), and
\item a positive lower bound $C_p |z|^d \le |p|$;
\end{itemize}
\item $q$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
\begin{itemize}
\item an upper bound $|q| \le C_q |z|^{d-1}$; and
\end{itemize}
\item $\mathcal{R}$ is an integral kernel operator
\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta, \]
where $k$ is a holomorphic function on $\Omega^2$, with
\begin{itemize}
\item an exponential upper bound $k(a, a') \le C_k e^{A|\zeta(a) - \zeta(a')|}$,
\item \textcolor{orange}{[bound K soft]} \[ | k (a, a') |\le \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} e^{\Lambda|\zeta(a)-\zeta(a')|}\]
\end{itemize}
\end{itemize}
Let $p_1$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$, and let $\tau = q_0 / p_1$.

@@

%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
\section{\textcolor{orange}{[Proof of main results]}}
\subsection{Overview}
\color{ForestGreen}
\begin{align*}
f & = \volterra f \\
f_\text{basic} + f_\text{extra} & = \volterra f_\text{basic} + \volterra f_\text{extra} \\
f_\text{basic} + f_\text{extra} & = \hardpart\,f_\text{basic} + \softpart \,f_\text{basic} + \volterra f_\text{extra} \\
f_\text{basic} + f_\text{extra} & = f_\text{basic} + \softpart \,f_\text{basic} + \volterra f_\text{extra} \\
f_\text{extra} & = \softpart \,f_\text{basic} + \volterra f_\text{extra}
\end{align*}
Solving the original equation is equivalent to finding a fixed point $f_\text{extra}$ of the affine-linear map
\[ \varphi \mapsto \softpart\,f_\text{basic} + \volterra \varphi. \]
\color{black}
\subsection{Solving the basic \textcolor{orange}{[prototype]} equation}
\subsubsection{Construction}

\begin{prop}
    Let $b\in\Omega$, the function 
    \begin{equation}%%\label{eqn:test_solution}
    f_0(a)=\frac{p(b)}{p(a)} \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]
   \end{equation}
is a solution of the Volterra equation $\volterra_{proto} f_0=f_0$. We call $f_0$ a prototype solution.  
\end{prop}

\begin{proof}
    Let $\Psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \Psi_0 = \frac{q}{p} \Psi_0 d\zeta $. Hence, for every $a\in\Omega$ 
    \begin{align*}
        \big[\volterra_{proto}f_0\big](a) &= \int_{\zeta=0}^{a} \frac{q}{p(a)} f_0 d\zeta \\
        &= \int_{\zeta=0}^{a} \frac{q}{p(a)} \frac{p(b)}{p}\Psi_0 d\zeta \\
        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \Psi_0 d\zeta\\
        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} d\Psi_0  \\
    \end{align*}
    Now we claim $\lim_{a\to 0}\Psi_0(a)=0$: in fact,
    \begin{align*}
        \Big\vert \exp\left(-\int_b^a\frac{q}{p}d\zeta\right) \Big\vert&\leq \exp\left(\int_b^a \Big\vert\frac{q}{p}\Big \vert\, |d\zeta|\right)\\
        &\leq \exp\left(\int_b^a \Big\vert\frac{q}{p}+\frac{\tau}{\zeta}\Big \vert\, |d\zeta| + \tau \int_b^a\frac{|d\zeta|}{|\zeta|} \right)\\
        &\Big\vert \frac{\zeta(a)}{\zeta(b)}\Big\vert^{\tau} \, \exp\left(\int_b^a \Big\vert\frac{q}{p}+\frac{\tau}{\zeta}\Big \vert\, |d\zeta|  \right)
    \end{align*}
    and by \textcolor{orange}{[limit assumption]}
\begin{align*}
     \Big\vert \exp\left(-\int_b^a\frac{q}{p}d\zeta\right) \Big\vert& \leq \Big\vert \frac{\zeta(a)}{\zeta(b)}\Big\vert^{\tau} \, \exp\Big(c |\zeta(a)-\zeta(b)|\Big)\\
     &\leq C |\zeta(a)|^\tau e^{c|\zeta(a)|}
\end{align*}
 which ends the proof of the claim. We deduce that $\volterra_{proto} f_0=f_0 $. 
\end{proof}

\subsubsection{Asymptotics}

@@

\begin{proof}
    We study separately the case when $\zeta(a)$ is close to the origin and far from the origin.  
\begin{itemize}
    \item \textbf{$\zeta(a)$ close to the origin.} We choose $\varepsilon>0$, then by \textcolor{orange}{[limit assumption]} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$
  \begin{equation}\label{eqn:limit_h1}
      \Big\vert\frac{q(a')}{p(a)}+\frac{\tau}{\zeta(a)}\Big\vert<\varepsilon
  \end{equation}
 % notice that $|p(a)|\leq \varepsilon$ for $|zeta(a)|\leq \delta$, while $|q(a')-\ell|\leq \varepsilon$ for $|\zeta(a')|\leq \delta$ and $\ell>0$. 
 Then, we choose $b\in\Omega$ such that $\tfrac{\delta}{2}=|\zeta(b)|$.
  \begin{align*}
      \left\vert\int_{\zeta(b)}^{\zeta(a)} \frac{p}{q}d\zeta\right\vert&\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q}{p}\Big\vert \, |d\zeta| \\
      &\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q}{p} +\frac{\tau}{\zeta}\Big\vert \, |d\zeta| +\int_{\zeta(b)}^{\zeta(a)} \Big\vert\frac{\tau}{\zeta}\Big\vert \, |d\zeta| \\
      &\leq \varepsilon \frac{\delta}{2} + \tau \log \Big\vert\frac{\zeta(a)}{\zeta(b)}\Big\vert
        \end{align*}

@@

\subsubsection{Image under $\softpart$}

>>>>

% hat tip TeX.SE user Andrew Stacey
%   https://tex.stackexchange.com/a/82503/6934
%   https://tex.stackexchange.com/questions/82425/tikz-radial-shading-of-a-ring#comment176908_82503
\pgfdeclareradialshading{radialedge}{\pgfpointorigin}{%
  color(0bp)=(transparent!0);
  color(20bp)=(transparent!0);
  color(22bp)=(transparent!10);
  color(24bp)=(transparent!90);
  color(25bp)=(transparent!100)
}
\pgfdeclarefading{radial edge}{\pgfuseshading{radialedge}}%

%%\theoremstyle{definition}
\newtheorem{defn}{Definition}
\theoremstyle{plain}
\newtheorem{prop}{Proposition}
\newtheorem{lem}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{rmk}{Remark}
\newtheorem{lemma}{Lemma}

% list formatting
\setlist[itemize]{leftmargin=24mm, rightmargin=12mm}
\makeatletter
% hat tip TeX.SE user31729
%   https://tex.stackexchange.com/a/328393/6934
\newcommand{\cond}[1]{\item[(\textsc{#1})]\protected@edef\@currentlabel{\textsc{#1}}}
\newcommand{\condconst}[2]{\item[($\text{\textsc{#1}} \mid #2$)]\protected@edef\@currentlabel{$\text{\textsc{#1}} \mid #2$}}
\makeatother

@@

If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically. \textbf{[...]}
\subsection{Setting}\label{setting}
\subsubsection{The domain}\label{setting:domain}
Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$. For some of our results, we'll need an extra condition on $\domain$:
\begin{itemize}
\cond{star}\label{cond:star} The set $\domain$ is star-shaped around $\zeta = 0$. In other words, for any $a \in \domain$, a straight path from $\zeta = 0$ to $a$ stays in $\domain$. Since $\domain$ doesn't contain $\zeta = 0$, we'll always leave that starting point out of the path.
\end{itemize}
For the applications we have in mind, $\domain$ might look something like the set pictured below, which satisfies Condition~\eqref{cond:star}.
\begin{center}
\begin{tikzpicture}
\newcommand{\spill}{4}
\fill[violet!20, bezier bounding box, path fading=radial edge]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (160:\spill)
  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
  arc (-60:-130:\spill) -- (0, 0);
\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = 0$};
\end{tikzpicture}
\end{center}
\subsubsection{The prototype operator}\label{setting:basic}
The prototypical example of the kind of operator we'll be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel and a regular singularity at $\zeta = 0$.

Being a holomorphic Volterra operator means that $\hardpart$ sends each holomorphic function $\varphi$ on $\domain$ to a new holomorphic function
\[ [\hardpart\,\varphi](a) = \int_{\zeta = 0}^a \hardker(a, \cdot)\,\varphi\;d\zeta. \]
Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We'll suppose this product can be written as a ratio
\[ \hardker(a, a') = \textcolor{magenta}{-} \frac{q(a')}{p(a)}, \]
where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means that for some constant $\tau$---the {\em residue} of the singularity---the difference
\[ \hardker(a, a') \textcolor{magenta}{-} \frac{\tau}{\zeta(a)} \]
is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\Omega^2$. We'll assume that $\tau$ is real and positive.

Our definition of a regular singularity implies that as $|\zeta|$ goes to zero, $|p|$ also goes to zero, while $|q|$ settles into a compact interval that doesn't include zero.
\begin{verify}
[\textit{Proof.} Fix any $a'$ in the neighborhood where the difference above is bounded. By confining $a$ to small enough neighborhoods of $\zeta = 0$, we can make $|\tau/\zeta(a)|$ arbitrarily large, forcing $|q(a')/p(a)|$ to become arbitrarily large to satisfy the definition. Since $a'$ is fixed, the only way for this ratio to get arbitrarily large is for $|p(a)|$ to get arbitrarily small.]
\end{verify}
For some of our results, we'll also need to keep $|p|$ and $|q|$ under control as $|\zeta|$ goes to infinity.
\begin{itemize}
%%\item[($\text{\textsc{slow}} \mid \lambda_0$)]
\condconst{slow}{\lambda_0}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
\begin{align*}
\left|\frac{1}{p}\right| & \lesssim e^{\lambda_p |\zeta|} &
\left|\frac{q}{p}\right| & \le \lambda_\text{ratio}
\end{align*}
outside some neighborhood of $\zeta = 0$ in $\Omega$. Note that this only constrains the ratio of $p$ and $q$ when they're evaluated at the same point. The constants will only enter our reasoning through their sum, $\lambda_0 = \lambda_p + \lambda_\text{ratio}$.
\end{itemize}
This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}. As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
\subsubsection{The perturbed operator}\label{setting:perturbed}
\color{RoyalBlue}
We'll generalize $\hardpart$ by adding a perturbation $\softpart$ that doesn't have a separable kernel, but does have a smoothing effect that counteracts the singularity of $\hardpart$. To get the smoothing effect, we'll require the kernel $\softker$ of $\softpart$ to vanish to some order $\epsilon > 0$ on the diagonal in $\Omega^2$. This requirement, combined with two others, will be made precise in Condition~\eqref{cond:eps-lambda}.

Since $\softpart$ is a holomorphic Volterra operator, $\softker$ is a holomorphic function on $\domain^2$. We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $p(a)^{-1}$ does, but we won't allow any sharper singularity. We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:slow} on $p$ and $q$. Altogether, we'll require:
\begin{itemize}
\condconst{diag}{\epsilon, \lambda}\label{cond:eps-lambda} We have
\[ \big| k_\text{extra} (a, a') \big| \lesssim \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$.
\end{itemize}
\color{black}

Our ultimate goal is the study of certain integral equations where the integral kernel is a perturbation of $k_\text{basic}$. In particular, we are interested in holomorphic Volterra operators $\volterra=\hardpart+\softpart$, hence the kernel $k_\text{extra}$ of $\softpart$ is a holomorphic function on $\Omega^2$.

For some of our results, we need to keep $k_\text{ext}$ under control at two different regimes: close to the point $\zeta=0$ and far toward infinity. In the former case, we require $k_\text{extra}$ to grow as $|\zeta|^{\epsilon-1}$ for some positive constant $\epsilon$; in the latter, we require $k_\text{ext}$ to be exponentially bounded
\begin{itemize}
\condconst{bounds}{\epsilon, \lambda}%%\label{cond:eps-lambda} (remove line break)
for every $a,a'\in\Omega$
\[ \big| k_\text{extra} (a, a') \big|\le C_{k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} e^{\lambda|\zeta(a)-\zeta(a')|}\]
\end{itemize}

Notice that if $a$ and $a'$ are close to $\zeta=0$, then the exponential factor is bounded and $k_\text{extra}(a,a')$ goes like $|\zeta(a)|^{\epsilon-1}$. Conversely, as $|\zeta(a)|$ goes to infinity (far from $\zeta=0$), the exponential term will be dominant because the polynomial growth of $|\zeta(a)|^{\epsilon-\tau}$ can be bounded by $e^{|\zeta(a)|}$.
\subsection{Main results}
%%\begin{defn}\label{fin-order}
%%Consider a Volterra operator $\mathcal{V}$ of the form
%%\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
%%We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
%%\begin{itemize}
%%\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
%%\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
%%\end{itemize}
%%and at one of the following holds:
%%\begin{enumerate}
%%\item\label{case:0th-order} $m$ isn't the zero function.
%%\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
%%\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
%%where {\rm ``diag''} means the diagonal in $\Omega^2$.
%%\end{enumerate}
%%We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
%%\end{defn}
\begin{thm}\label{thm:basic_volterra}
For a regular singular Volterra equation
\[ f = \hardpart f \]
involving the kind of operator described in Section~\ref{setting:basic}, we have the {\em prototype solution}
\begin{equation}\label{eqn:test_solution}
f_0(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.

The solution $f_0$ scales like $\zeta^{\tau-1}$ as $\zeta$ goes to $0$. To be precise, as $\zeta$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
\end{thm}
\begin{thm}
Suppose $\hardpart$ satisfies Condition~\eqref{cond:slow} from Section~\ref{setting:basic}. Then the solution $f_0$ from Theorem~\ref{thm:basic_volterra} is uniformly of exponential type $\lambda_0$ \textcolor{orange}{[explain what we mean by ``uniformly'']}. In light of the behavior at $\zeta = 0$ described above, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}
\begin{thm}\label{thm:perturbed_volterra}
\textcolor{DarkTurquoise}{Existence and uniqueness for perturbed operator}
Let $g$ be a function in the space $\in\singexp{\sigma+\epsilon}{A}(\Omega)$ defined in Section~\ref{fn-spaces}. The Volterra equation
\[ f = \Big[\hardpart +\softpart \Big] f + g \]
given by an operator of the kind described in Sections \ref{setting:basic} and \ref{setting:perturbed}, admits a unique solution $f$ that belongs to $\singexp{\sigma+\epsilon}{\Lambda}(\Omega)$, for every $\Lambda\geq A$ \textcolor{magenta}{[check]}. 
\end{thm}

\textcolor{DarkTurquoise}{The result below might not be stated perfectly, but it gives at least a rough sense of what I expect. It's an improved version of the result stated in Section~\ref{frac_int_exist}, which is copied from {\tt airy-resurgence}. Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}
\color{RoyalBlue}
\begin{thm}
Let $\Omega$ be an acute-angled open sector around $\zeta = 0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.} Over $\Omega$, consider a Volterra operator
\[ \mathcal{P} = p + \partial^{-1} \circ q + \mathcal{R}, \]
where
\begin{itemize}
\item $p$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
\begin{itemize}
\item a simple zero at $\zeta = 0$,
\item no zeros in $\Omega$ (as the next condition implies), and
\item a positive lower bound $C_p |z|^d \le |p|$;
\end{itemize}
\item $q$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
\begin{itemize}
\item an upper bound $|q| \le C_q |z|^{d-1}$; and
\end{itemize}
\item $\mathcal{R}$ is an integral kernel operator
\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta, \]
where $k$ is a holomorphic function on $\Omega^2$, with
\begin{itemize}
\item an exponential upper bound $k(a, a') \le C_k e^{A|\zeta(a) - \zeta(a')|}$,
\item \textcolor{orange}{[bound K soft]} \[ | k (a, a') |\le \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} e^{\Lambda|\zeta(a)-\zeta(a')|}\]
\end{itemize}
\end{itemize}
Let $p_1$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$, and let $\tau = q_0 / p_1$.

@@

%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.

\section{Construction and regularity of the prototype solution}

\subsection{Construction}\label{sec:construction}

\begin{prop}
    Let $b\in\Omega$, the function 
    \begin{equation}%%\label{eqn:test_solution}
    f_0(a)=\frac{p(b)}{p(a)} \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]
   \end{equation}
is a solution of the Volterra equation $\hardpart f_0=f_0$. We call $f_0$ a prototype solution.  
\end{prop}

\begin{proof}
    Let $\Psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \Psi_0 = - \frac{q}{p} \Psi_0 d\zeta $. Hence, for every $a\in\Omega$ 
    \begin{align*}
        \big[\hardpart f_0\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} f_0 d\zeta \\
        &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} \frac{p(b)}{p}\Psi_0 d\zeta \\
        &= - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \Psi_0 d\zeta\\
        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} d\Psi_0  \\
    \end{align*}
    Now we claim $\lim_{a\to 0}\Psi_0(a)=0$: in fact,
    \begin{align*}
        \Big\vert \exp\left(-\int_b^a\frac{q}{p}d\zeta\right) \Big\vert&\leq \exp\left(\int_b^a \Big\vert\frac{q}{p}\Big \vert\, |d\zeta|\right)\\
        &\leq \exp\left(\int_b^a \Big\vert\frac{q}{p}\textcolor{magenta}{-}\frac{\tau}{\zeta}\Big \vert\, |d\zeta| + \tau \int_b^a\frac{|d\zeta|}{|\zeta|} \right)\\
        &\Big\vert \frac{\zeta(a)}{\zeta(b)}\Big\vert^{\tau} \, \exp\left(\int_b^a \Big\vert\frac{q}{p}\textcolor{magenta}{-}\frac{\tau}{\zeta}\Big \vert\, |d\zeta|  \right)
    \end{align*}
    and by \textcolor{orange}{[limit assumption]}
\begin{align*}
     \Big\vert \exp\left(-\int_b^a\frac{q}{p}d\zeta\right) \Big\vert& \leq \Big\vert \frac{\zeta(a)}{\zeta(b)}\Big\vert^{\tau} \, \exp\Big(c |\zeta(a)-\zeta(b)|\Big)\\
     &\leq C |\zeta(a)|^\tau e^{c|\zeta(a)|}
\end{align*}
 which ends the proof of the claim. We deduce that $\hardpart  f_0=f_0 $. 
\end{proof}

\subsection{Asymptotics}\label{sec:asymptotics}

@@

\begin{proof}
    We study separately the case when $\zeta(a)$ is close to the origin and far from the origin.  
\begin{itemize}
    \item \textbf{$\zeta(a)$ close to the origin.} We choose $\varepsilon>0$, then by \textcolor{orange}{[limit assumption]} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$
  \begin{equation}\label{eqn:limit_h1}
      \Big\vert\frac{q(a')}{p(a)}\textcolor{magenta}{-}\frac{\tau}{\zeta(a)}\Big\vert<\varepsilon
  \end{equation}
 % notice that $|p(a)|\leq \varepsilon$ for $|zeta(a)|\leq \delta$, while $|q(a')-\ell|\leq \varepsilon$ for $|\zeta(a')|\leq \delta$ and $\ell>0$. 
 Then, we choose $b\in\Omega$ such that $\tfrac{\delta}{2}=|\zeta(b)|$.
  \begin{align*}
      \left\vert\int_{\zeta(b)}^{\zeta(a)} \frac{p}{q}d\zeta\right\vert&\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q}{p}\Big\vert \, |d\zeta| \\
      &\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q}{p} \textcolor{magenta}{-} \frac{\tau}{\zeta}\Big\vert \, |d\zeta| +\int_{\zeta(b)}^{\zeta(a)} \Big\vert\frac{\tau}{\zeta}\Big\vert \, |d\zeta| \\
      &\leq \varepsilon \frac{\delta}{2} + \tau \log \Big\vert\frac{\zeta(a)}{\zeta(b)}\Big\vert
        \end{align*}

@@

\section{Existence and uniqueness of solutions of the perturbed equation}

\subsection{Image under $\softpart$}\label{sec:image under soft_part}
